Capstone Movielens Report

### 2025-05-25 reports/templates/02.X.UM+model.template.Rmd
Section `UMGYE Model Building` completed.

#### [calc_UM?_effect_MSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM?-effect.functions.R#L93) Function
\

@@

#### [calc_UM?_effect_MSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM?-effect.functions.R#L119) Function
\

@@

#### [calc_UM?_effect_RMSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM?-effect.functions.R#L115) Function
\

@@

#### [calc_UM?_effect_RMSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM?-effect.functions.R#L119) Function
\

>>>>

#### [calc_UM?_effect_MSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM?-effect.functions.R#L93) Function {#func.calc_UM?_effect_MSE}
\

@@

#### [calc_UM?_effect_MSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM?-effect.functions.R#L119) Function {#func.calc_UM?_effect_MSE.cv}
\

@@

#### [calc_UM?_effect_RMSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM?-effect.functions.R#L115) Function {#func.calc_UM?_effect_RMSE}
\

@@

#### [calc_UM?_effect_RMSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM?-effect.functions.R#L119) Function {#func.calc_UM?_effect_RMSE.cv}
\
